### 2016-07-05 ch03-lrm/nonparametric.tex
Small changes, mostly removal of TODOs

\section{Introduction}
\label{sec:nonparametric:introduction}
%TODO: go back further in time for refs

Whereas many areas of system identification focus on parametric identification and/or parameter estimation, non-parametric techniques have received renewed interest from the community over the last decade.
One of the reasons for this is that non-parametric techniques typically require fewer assumptions and knowledge of the system than building parametric models.
As a consequence, non-parametric methods are often more robust than fully parametric methods.
Besides, \glspl{FRF} have been shown to provide a quick insight into the basic dynamic properties of \gls{LTI} systems.
This capability is very useful for system design, manual controller tuning, model validation and model selection for parametric models~\citep{Pintelon2012}.

>>>>

\section{Introduction}
\label{sec:nonparametric:introduction}
Whereas many areas of system identification focus on parametric identification and/or parameter estimation, non-parametric techniques have received renewed interest from the community over the last decade.
One of the reasons for this is that non-parametric techniques typically require fewer assumptions and knowledge of the system than building parametric models.
As a consequence, non-parametric methods are often more robust than fully parametric methods.
Besides, \glspl{FRF} have been shown to provide a quick insight into the basic dynamic properties of \gls{LTI} systems.
This capability is very useful for system design, manual controller tuning, model validation and model selection for parametric models~\citep{Pintelon2012}.
